Revisited hidden weight bit function

### 2024-11-07 RevisedHiddenWeight.tex
Typos in proof of Theorem 3

    Therefore, in case $\lambda<\frac 16$, we can conclude from the two claims that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and this maximum is then equal to $2^{2-2\lambda}=2^{2\mu}$, as required. For $\lambda=\frac 16$, the solution to the equation $\mathcal E$ is $\cos\alpha=1$, again implying that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and we obtain the same maximum of $2^{2\mu}$. In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the two values $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$.

    \pmnote{@Tim, is the expression of $\cos(2\alpha_0)$ correct in the following? I think it should be $4\lambda^2-4 \lambda \sqrt{bla} - 8\lambda +3$ instead, which is coherent with the next expression}

     For such $\alpha$, the double angle formula for the cosine implies that $\cos(2\alpha_0)=2\lambda^2-4\lambda+2-2\lambda\sqrt{\lambda^2-4\lambda+2}$. If we replace $\cos\alpha_0$ and $\cos(2\alpha_0)$ by their respective values, we obtain that the maximum of $g(\alpha)$ for $\alpha\in[0,\pi]$ is given by the following value:

    \[
        g(\alpha_0)=\frac{\left(-8\lambda^2+16\lambda+8\lambda\sqrt{\lambda^2-4\lambda+2}\right)^{\lambda}}{\left(2-2\lambda+2\sqrt{\lambda^2-4\lambda+2}\right)^{2\lambda-1}}=2^{2\mu}.
    \]
    %This is exactly what we wanted to prove, 
    This is equivalent to the first equation in the theorem statement, 
    and we have therefore covered the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$ entirely. In a similar fashion, it can be proven that $|P_{a,t}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$ for the remaining two cases of $(p,q,r;u,v)$. In fact, for $(p,q,r;u,v)=(0,t,0;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_1(\alpha)=(6-2\cos(2\alpha))^\lambda(2-2\cos\alpha)^{1-2\lambda}$, which has the same maximum as $g(\alpha)$ because $h_1\left(\frac{\pi}{2}+\alpha\right)=g\left(\frac{\pi}{2}-\alpha\right)$; for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_2(\alpha)=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ because $h_2(\alpha)\leq g(\alpha)$.
\end{proof}

>>>>

    Therefore, in case $\lambda<\frac 16$, we can conclude from the two claims that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and this maximum is then equal to $2^{2-2\lambda}=2^{2\mu}$, as required. For $\lambda=\frac 16$, the solution to the equation $\mathcal E$ is $\cos\alpha=1$, again implying that $g(\alpha)$ reaches its maximum at $\alpha_0=0$, and we obtain the same maximum of $2^{2\mu}$. In case $\lambda>\frac 16$, the two claims imply that $g(\alpha)$ reaches its maximum at the unique $\alpha_0\in[0,\pi]$ for which $\cos\alpha_0=-\lambda+\sqrt{\lambda^2-4\lambda+2}$. For this $\alpha_0$, the double angle formula for the cosine implies that $\cos(2\alpha_0)=4\lambda^2-8\lambda+3-4\lambda\sqrt{\lambda^2-4\lambda+2}$. If we replace $\cos\alpha_0$ and $\cos(2\alpha_0)$ by their respective values, we obtain that the maximum of $g(\alpha)$ for $\alpha\in[0,\pi]$ is given by the following value:
    \[
        g(\alpha_0)=\frac{\left(-8\lambda^2+16\lambda+8\lambda\sqrt{\lambda^2-4\lambda+2}\right)^{\lambda}}{\left(2-2\lambda+2\sqrt{\lambda^2-4\lambda+2}\right)^{2\lambda-1}}=2^{2\mu}.
    \]
    %This is exactly what we wanted to prove, 
    This is equivalent to the first equation in the theorem statement, 
    and we have therefore covered the case $(p,q,r;u,v)=(t,0,0;n-2t,0)$ entirely. In a similar fashion, it can be proven that $|P_{a,t}(z)|$ is also bounded by $2^{\mu n}$ on $\dis$ for the remaining two cases of $(p,q,r;u,v)$. In fact, for $(p,q,r;u,v)=(0,t,0;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_1(\alpha)=(6-2\cos(2\alpha))^\lambda(2-2\cos\alpha)^{1-2\lambda}$, which has the same maximum as $g(\alpha)$ because $h_1\left(\frac{\pi}{2}+\alpha\right)=g\left(\frac{\pi}{2}-\alpha\right)$; for $(p,q,r;u,v)=(0,0,t;n-2t,0)$, it is enough to replace $g(\alpha)$ by $h_2(\alpha)=(2+2\cos(2\alpha))^\lambda(2+2\cos\alpha)^{1-2\lambda}$, whose maximum is bounded by the maximum of $g(\alpha)$ because $h_2(\alpha)\leq g(\alpha)$.
\end{proof}
